\documentclass[10pt]{article}

\input{preamb}
\usepackage[english]{babel}
\usepackage{xeCJK}

%\usepackage{ctex}
\usepackage{marvosym,multirow}
\usepackage[T1]{fontenc}
%\usepackage{fontawesome}
\usepackage[colorlinks = true,
            linkcolor = Blue,
            urlcolor  = Blue,
            citecolor = Blue,
            anchorcolor = Blue]{hyperref}
\usepackage{multicol}

\newenvironment{myitemize}
{ \begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  } 
\usepackage{enumitem}
\setlist[enumerate]{itemsep=0mm}

\usepackage{etaremune}
%===================================================

\begin{document}

%\begin{multicols}{2}
\section*{{\huge ZHANG, Kai\quad  张 凯}} 

\vspace{-0.6in}
\null\hfill {\scriptsize Updated:  \selectlanguage{english} \today}

\begin{center}
\rule{\textwidth}{0.5pt}
\end{center}
\vspace{-0.34in}
~\\

\noindent Associate Professor (Tenure Track)\\ 
Department of Civil Engineering\\
School of Naval Architecture, Ocean and Civil Engineering\\
Shanghai Jiao Tong University, Shanghai, 200240\\
~\\
E-mail: \href{kai.zhang@sjtu.edu.cn}{kai.zhang@sjtu.edu.cn}\\
Personal Website: \href{https://zhang-kai.xyz}{https://zhang-kai.xyz} \\
Google Scholar: \href{https://scholar.google.com/citations?user=xQ9TdtgAAAAJ&hl=en}{https://scholar.google.com/citations?user=xQ9TdtgAAAAJ\&hl=en}\\

\vspace{-0.34in}
\begin{center}
\rule{\textwidth}{0.5pt}
\end{center}

\subsection*{Research Interests}

\begin{multicols}{2}
\begin{myitemize}
\item Bluff Body Aerodynamics
\item Computational Fluid Dynamics
\item Flow Control
\item Reduced-Order Modeling
\item Data-Driven Analysis
\item Linear Stability Analysis


\end{myitemize}
\end{multicols}

\subsection*{Education}

{\bf\color{Blue} Yokohama National University, Yokohama, Japan}		
\begin{myitemize}
\item Doctor of Engineering, Oct. 2014 -- Sept. 2017.
\item Master of Engineering, Oct. 2012 -- Sept. 2014.\\
\textit{Department of Civil Engineering, Graduate School of Urban Innovation}
\end{myitemize}
{\bf\color{Blue} Shanghai Jiao Tong University, Shanghai, China}
\begin{myitemize}
\item Master Candidate, Sept. 2011 -- Sept. 2012.\\
\textit{Department of Civil Engineering, School of Naval Architecture, Ocean and Civil Engineering}
\end{myitemize}
{\bf\color{Blue} Xi'an Jiao Tong University, Xi'an, China}
\begin{myitemize}
\item Bachelor of Engineering, Sept. 2007 -- Aug. 2011.\\
\textit{Department of Civil Engineering, School of Human Settlement and Civil Engineering}
\end{myitemize}

\subsection*{Appointments}

{\bf \color{Blue} Shanghai Jiao Tong University, Shanghai, China} 
\begin{myitemize}
\item Associate Professor, Feb. 2022 -- present \\
{\em School of Naval Architecture, Ocean and Civil Engineering}
\end{myitemize}
{\bf \color{Blue} Rutgers University, New Brunswick, NJ, USA} 
\begin{myitemize}
\item  Postdoctoral research associate, Mar. 2020 -- Jan .2022\\
{\em Department of Mechanical and Aerospace Engineering}
\end{myitemize}
{\bf \color{Blue} University of California, Los Angeles, CA, USA} 
\begin{myitemize}
\item  Postdoctoral research associate, Jan. 2019 -- Feb. 2020\\
{\em Department of Mechanical and Aerospace Engineering}
\end{myitemize}
\noindent {\bf \color{Blue} Florida State University, Tallahassee, FL, USA} 
\begin{myitemize}
\item Postdoctoral research associate, Nov. 2017 -- Dec. 2018 \\
{\em Department of Aerospace and Mechanical Engineering}
\end{myitemize}

%\subsection*{Teaching}
%{\bf \color{Blue}Shanghai Jiao Tong University}
%	\begin{myitemize}
%	\item Spring 2022: Bluff Body Aerodynamics (Graduate)
%	\item Fall 2022: Data-Driven Fluid Dynamics (Graduate)
%	\end{myitemize}


%\subsection*{Honors and Awards}
%\begin{myitemize}
%\item SIAM-CSE Early Career Travel Award, NSF, 2021 
%\item Amelia Earhart Fellowship, Zonta International, 2016 
%\item Travel Award for Excellence in Graduate Research, American Physics Society, 2013
%\item Excellent Student of Academic Records Scholarship, HUST, 2009-2011
%\item Scholarship for Outstanding Leadership of Student Union, HUST, 2011
%%\item First Prize for English Speech Contest, HUST, 2009 
%\end{myitemize}
%
%\subsection*{Selected Student Honors and Awards}
%\begin{myitemize}
%\item Undergraduate student Kee Horng Seh received SOURCE Grant for his project {\it``Numerical Investigation of Hydrodynamic Flow Over Orthoconic Structure with Annulation"}. (2021)
%%\item Undergraduate student Kee Horng Seh was selected to participate in Invent@SU invention and entrepreneurship accelerator program. (2021)
%\end{myitemize}
%
%\subsection*{Grants and Contracts}
%{\bf Bolded: active grants/contracts}
%~\\
%
%\noindent {\bf \color{Blue}Syracuse University}
%\begin{myitemize}
%\item {\bf Characterizing Hydrodynamic Properties of Flow over Shell Sculpture in Orthoconic Cephalopods: Finding New Solutions for Drag Reduction, Stability, and Biofouling\\
%(Innovative \& Interdisciplinary Research, CUSE)\\
%$~~~~~~$PI with L. Ivany and M. A. Green, 06/2021-05/2023, \$23,742}
%
%\end{myitemize}



\vspace{-0.1in}
\subsection*{Academic Services}
{\bf \color{Blue}Reviewer of Journal Articles}
\vspace{-0.05in}
	\begin{myitemize}
 \item Journal of Fluid Mechanics
	\item AIAA Journal
 \item Theoretical and Computational Fluid Dynamics
	\item Physics of Fluids
	\item Journal of Nuclear Science and Technology
	\item Journal of Fluids Engineering

	\end{myitemize}



\subsection*{Publications}
{\bf \color{Blue}Journal Articles} (*  Corresponding author)
{\small
\begin{etaremune}
 \item [] {\bf \color{Blue} In Review \rule{13.8cm}{0.2mm}} 

 \item Tu, Y., \textbf{Zhang, K.}*, Han, Z., Zhou, D. \& Bilgen, O. (2022) Aerodynamic characterization of two tandem wind turbines under yaw misalignment control using actuator line model. Submitted.
 
 \item \textbf{Zhang, K.}, Bao, Y., Zhou, D. \& Han, Z. (2022) End boundary effects on wakes dynamics of inclined circular cylinders. Submitted.
 
 \item \textbf{Zhang, K.}, Zhu, H., Cao, Y. \& Zhou, D.(2022) Reynolds number effects on the bistable flows over a wavy circular cylinder. Submitted.



 
 \item [] {\bf \color{Blue} 2022 \rule{14.8cm}{0.2mm}}
 
 \item Ping, H., Cao, Y., \textbf{Zhang, K.}, Han, Z., Zhou, D., Zhu, H. \& Bao, Y. (2022) Vortex-induced vibrations of two rigidly coupled circular cylinders in tandem arrangement. \textit{\textbf{Ocean Engineering}}, 263, 112316. 
 
 \item Marques Ribeiro, J. H., Yeh, C.-A., \textbf{Zhang, K.} \& Taira, K. (2022) Wing sweep effect on laminar separated flows.  \textit{\textbf{Journal of Fluid Mechanics}}, accepted. 

 \item \textbf{Zhang, K.}* \& Haque, N. (2022) Wake interactions between two side-by-side circular cylinders of uneven size.  \textit{\textbf{Physical Review Fluids}}, 7, 064703.

  \item Burtsev, A., He, W., Hayostek, S., \textbf{Zhang, K.}, Theofilis, V., Taira, K. \& Amitay, M. (2022) Linear modal instabilities around post-stall swept finite aspect ratio wings at low Reynolds numbers. \textit{\textbf{Journal of Fluid Mechanics}}, 944, A6.

  \item \textbf{Zhang, K.}*, Taira, K. (2022) Laminar vortex dynamics around forward-swept wings.  \textit{\textbf{Physical Review Fluids}}, 7, 024704.

  \item \textbf{Zhang, K.}*, Shah, B. and Bilgen, O. (2022) Low-Reynolds-number aerodynamic characteristics of airfoils with piezocomposite trailing control surfaces. \textit{\textbf{AIAA Journal}}, 60(4), 2701-2706.

	\item Kuang, L., Su, J., Chen, Y., Han, Z., Zhou, D., \textbf{Zhang, K.}, Zhao, Y. \& Bao, Y. (2021). Wind-capture-accelerate device for performance improvement of vertical-axis wind turbines: External diffuser system. \textit{\textbf{Energy}}, 239(B), 15, 122196. 

\item [] {\bf \color{Blue} 2021 \rule{14.8cm}{0.2mm}}

  \item Morimoto, M., Fukami, K., \textbf{Zhang, K.} \& Fukagata, K. (2021). Toward practical uses of neural networks for fluid flow estimation. \textit{\textbf{Neural Computing and Applications}}, 34(5), 3647-3669.

  \item Ping, H., Zhu, H., \textbf{Zhang, K.}, Zhou, D., Bao, Y. \& Han, Z. (2021). Vortex-induced vibrations of two rigidly coupled circular cylinders of unequal diameters at low Reynolds number. \textit{\textbf{Physics of Fluids}}, 33, 103603. 
  
  \item Fukami, K., Murata, T., \textbf{Zhang, K.} \& Fukagata, K. (2021). Sparse identification of nonlinear dynamics with low-dimensionalized flow representations. \textit{\textbf{Journal of Fluid Mechanics}}, 926, A10.
  
  \item Morimoto, M., Fukami, K., \textbf{Zhang, K.}, Nair, A. G. \& Fukagata, K. (2021). Convolutional neural networks for fluid flow analysis: toward effective metamodeling and low-dimensionalization. \textit{\textbf{Theoretical and Computational Fluid Dynamics}}, 35, 633–658.

  \item Ping, H., Zhu, H., \textbf{Zhang, K.}, Zhou, D., Bao, Y., Xu, Y. \& Han, Z. (2021). Dynamic mode decomposition based analysis of flow past a transversely oscillating cylinder. \textit{\textbf{Physics of Fluids}}, 33, 033604. 
  
  \item Zhang, Z., Tu, J., \textbf{Zhang, K.}, Yang, H., Han, Z., Zhou, D., Xu, J. \& Zhang, M. (2021). Vortex characteristics and flow-induced forces of the wavy cylinder at a subcritical Reynolds number. \textit{\textbf{Ocean Engineering}}, 222, 108593.
  
  \item Chen, Y., Dong, Z., Wang, Y., Su, J., Zhou, D., \textbf{Zhang, K.}, Zhao, Y., Bao, Y. \& Han, Z. (2021). Short-term wind speed predicting framework based on EEMD-GA-LSTM method under large scaled wind history. \textit{\textbf{Energy Conversion and Management}}, 227, 113559.
  
 \item [] {\bf \color{Blue} 2020 \rule{14.8cm}{0.2mm}} 
 
  \item Ping, H., Zhu, H., \textbf{Zhang, K.}, Wang, R., Zhou, D., Bao, Y. \& Han, Z. (2020). Wake dynamics behind a rotary oscillating cylinder analyzed with proper orthogonal decomposition. \textit{\textbf{Ocean Engineering}}, 218, 108185.
  
  \item \textbf{Zhang, K.}$^*$, Hayostek, S., Amitay, M., Burtsev, A., Theofilis, V. \& Taira, K. (2020). Laminar separated flows over finite-aspect-ratio swept wings. \textit{\textbf{Journal of Fluid Mechanics}}, 905, R1.
  
  \item \textbf{Zhang, K.}, Zhou, D., Katsuchi, H., Yamada, H., Han, Z. \& Bao, Y. (2020). Bistable states in the wake of a wavy cylinder. \textit{\textbf{Physics of Fluids}}, 32(7), 074112.
  
  \item \textbf{Zhang, K.}$^*$, Hayostek, S., Amitay, M., He, W., Theofilis, V. \& Taira, K. (2020). On the formation of three-dimensional separated flows over wings under tip effects. \textit{\textbf{Journal of Fluid Mechanics}}, 895, A9.

 \item [] {\bf \color{Blue} 2018 \rule{14.8cm}{0.2mm}} 

  \item \textbf{Zhang, K.}, Katsuchi, H., Zhou, D., Yamada, H., Bao, Y., Han, Z. \& Zhu, H. (2018). Numerical study of flow past a transversely oscillating wavy cylinder at $Re$= 5000. \textit{\textbf{Ocean Engineering}}, 169, 539-550.
  
  \item \textbf{Zhang, K.}, Katsuchi, H., Zhou, D., Yamada, H. \& Lu, J. (2018). Large eddy simulation of flow over inclined wavy cylinders. \textit{\textbf{Journal of Fluids and Structures}}, 80, 179-198.
  
  \item Ma, N., Lei, H., Han, Z., Zhou, D., Bao, Y., \textbf{Zhang, K.}, Zhou, L. \& Chen, C. (2018). Airfoil optimization to improve power performance of a high-solidity vertical axis wind turbine at a moderate tip speed ratio. \textit{\textbf{Energy}}, 150, 236-252.
  
  \item He, T., Zhang, H. \& \textbf{Zhang, K.} (2018). A smoothed finite element approach for computational fluid dynamics: applications to incompressible flows and fluid–structure interaction. \textit{\textbf{Computational Mechanics}}, 62(5), 1037-1057.

 \item [] {\bf \color{Blue} 2017 \rule{14.8cm}{0.2mm}}   

  \item Ma, J., Zhou, D., Han, Z., \textbf{Zhang, K.}, Nguyen, J., Lu, J. \& Bao, Y. (2017). Numerical simulation of fluctuating wind effects on an offshore deck structure. \textit{\textbf{Shock and Vibration}}, 2017.
  \item He, T., \textbf{Zhang, K.} \& Wang, T. (2017). AC-CBS-based partitioned semi-implicit coupling algorithm for fluid-structure interaction using stabilized second-order pressure scheme. \textit{\textbf{Communications in Computational Physics}}, 21(5), 1449-1474.
  
  \item \textbf{Zhang, K.}, Katsuchi, H., Zhou, D., Yamada, H., Zhang, T. \& Han, Z. (2017). Numerical simulation of vortex induced vibrations of a flexibly mounted wavy cylinder at subcritical Reynolds number. \textit{\textbf{Ocean Engineering}}, 133, 170-181.
  
  \item He, T. \& \textbf{Zhang, K.} (2017). An overview of the combined interface boundary condition method for fluid–structure interaction. \textit{\textbf{Archives of Computational Methods in Engineering}}, 24(4), 891-934.
  
 \item [] {\bf \color{Blue} Before 2016 \rule{13.6cm}{0.2mm}}   

  \item \textbf{Zhang, K.}, Katsuchi, H., Zhou, D., Yamada, H. \& Han, Z. (2016). Numerical study on the effect of shape modification to the flow around circular cylinders. \textit{\textbf{Journal of Wind Engineering and Industrial Aerodynamics}}, 152, 23-40.  

  \item He, T. \& \textbf{Zhang, K.} (2015). Combined interface boundary condition method for fluid–structure interaction: Some improvements and extensions. \textit{\textbf{Ocean Engineering}}, 109, 243-255.
  
  \item Tu, J., Zhou, D., Bao, Y., Fang, C., \textbf{Zhang, K.}, Li, C., \& Han, Z. (2014). Flow-induced vibration on a circular cylinder in planar shear flow. \textit{\textbf{Computers and Fluids}}, 105, 138-154.

\end{etaremune}
}

\vspace{+0.1in}
{\bf \color{Blue}Conference Papers}

{\small
\begin{etaremune}

\item \textbf{Zhang, K.} and Taira, K. Aerodynamic characterization of low-aspect-ratio swept wings at $Re=400$. \textit{\textbf{AIAA SciTech}}. San Diego, CA. Jan. 3-7, 2022.

\item Morimoto, M., Fukami, K., \textbf{Zhang, K.} and K. Fukagata. Toward practical machine learning and fluid flow regressions: perspective on interpretability and generalizability. \textit{\textbf{JSFM 34th Symposium of Computational Fluid Dynamics}}. Okinawa, Japan. Dec. 2020.

\item \textbf{Zhang, K.} and Bilgen, O. Multi-fidelity aerodynamic modeling of a floating offshore wind turbine rotor. \textit{\textbf{International Mechanical Engineering Congress \& Exposition}}. Online. Nov. 2020.

\item Hayostek, S., Amitay, M., \textbf{Zhang, K.}, Taira, K., He, W. and Theofilis, V. Wake dynamics of finite aspect ratio wings. Part I: An experimental study. \textit{\textbf{AIAA SciTech}}. San Diego, CA. Jan. 7-11, 2019.

\item \textbf{Zhang, K.}, Taira, K., Hayostek, S., Amitay, M., He, W. and Theofilis, V. Wake dynamics of finite aspect ratio wings. Part II: Computational study. \textit{\textbf{AIAA SciTech}}. San Diego, CA. Jan. 7-11, 2019.

\item He, W., Burtsev, A., Theofilis, V. \textbf{Zhang, K.}, Taira, K., Hayostek, S. and Amitay, M. Wake dynamics of finite aspect ratio wings. Part III: TriGlobal linear stability study.
 \textit{\textbf{AIAA SciTech}}. San Diego, CA. Jan. 7-11, 2019.

\item Hayostek, S., Amitay, M., \textbf{Zhang, K.}, Taira, K., He, W., Burtsev, A. and Theofilis, V. Collaborative investigation of 3-D separation on low aspect ratio finite span wings.
 \textit{\textbf{59th Israel Annual Conference on Aerospace Sciences}}. Tel Aviv and Haifa, Israel. March 2019.

\item Taira, K., \textbf{Zhang, K.}, Amitay, M., Hayostek, S., Theofilis, V., He, W. and Burtsev, A. Separated flows over finite-aspect-ratio wings: computational, experimental, and stability analyses. \textit{\textbf{11th International Symposium on Turbulence and Shear Flow Phenomenon}}. Southampton, UK. Jul. 2019.

\item \textbf{Zhang, K.}, Zhou, D., Katsuchi, H., Yamada, H., Bao, Y. and Han, Z. Free and forced vibration of a wavy cylinder in cross-flow direction. \textit{\textbf{7th Conference on Bluff Body Wakes and Vortex-Induced Vibrations}}. Marseille, France. Jul. 2018.

\item \textbf{Zhang, K.}, Katsuchi, H., Yamada, H. and Zhou, D. On the fluid dyanmics of circular cylinders with spanwise waviness. \textit{\textbf{the 7th European-African Conference on Wind Engineering}}. Liege, Belgium. Jul. 2017.

\item \textbf{Zhang, K.}, Zhou, D., Katsuchi, H., and Yamada, H. Numerical study of flow around circular cylinders with shape modification. \textit{\textbf{14th International Symposium on Structural Engineering}}. Beijing, China. Oct. 2016.

\item \textbf{Zhang, K.}, Zhou, D., Katsuchi, H., and Yamada, H. Numerical investigation of vortex induced vibration of wavy cylinders. \textit{\textbf{IASS Annual Symposium}}. Tokyo, Japn. Sep. 2016.

\item \textbf{Zhang, K.}, Katsuchi, H., Zhou, D. \& Yamada, H. Numerical investigation of vortex induced vibration of wavy cylinders. \textit{\textbf{8th International Colloquium on Bluff Body Aerodyanmics and Applications}}. Boston, Massachusetts, USA. Jun. 2016.

\item \textbf{Zhang, K.}, Katsuchi, H., Zhou, D., Yamada, H. \& Han, Z. Large eddy simulation of flow around circular cylinders with shape modification. \textit{\textbf{14th International Conference on Wind Engineering}}, Porto Alegre, Brazil. Jun. 2015.

\end{etaremune}

}

{\bf \color{Blue}Presentations} 

{\small
\begin{etaremune}

\item \textbf{Zhang, K.} and Taira, K. Effect of sweep on the laminar separated flows over finite-aspect-ratio wings. \textit{\textbf{APS Division of Fluid Dynamics Meeting}}, Seattle, WA. Nov. 2019.

\item \textbf{Zhang, K.} and Taira, K. Three-dimensional flow over finite-aspect-ratio wings. \textit{\textbf{13th Southern California Flow Physics Symposium}}, Santa Babara, CA. Apr. 2019.

\item \textbf{Zhang, K.} and Taira, K. Tip effects on three-dimensional wake dynamics over high-incidence finite-aspect-ratio wings. \textit{\textbf{APS Division of Fluid Dynamics Meeting}}, Atlanta, GA. Nov. 2018.

\end{etaremune}
}



\subsection*{Advising}
\noindent {\bf \color{Blue}Current Ph.D. students}
\begin{myitemize}
\itemsep0.5em 
\item TU, Yu 【涂瑜】 (with Prof. D. Zhou and Prof. Z. Han), 2021 -- present 
%\item BAI, Jiong-Zhuo 【白炅卓】,   2023 -- present
\end{myitemize}

%\noindent {\bf \color{Blue}Current M.S. students}
%\begin{myitemize}
%\item 2023 -- present, SHANG, Xiao-Zhen 【尚晓朕】, 2023 -- present
%\end{myitemize}


%\noindent {\bf \color{Blue}Ph.D. thesis Committee} (*: chair, $\dagger$: work defended)
%\begin{myitemize}
%\item Emma Dawn Gist, Aerospace Engineering, Syracuse University, {\it ``TBD".} (Advisor: Dr.~Mark Glauser)
%\item 2021 Yuyan Hao, Mechanical and Aerospace Engineering, Syracuse University, {\it ``TBD".} (Advisor: Dr.~John F. Dannenhoffer)
%\item 2021 Seth Brooks$^\dagger$, Mechanical and Aerospace Engineering, Syracuse University, {\it ``Analysis of Multiple Degree-of-freedom Oscillatory Aquatic Propulsion".} (Advisor: Dr.~Melissa Green)
%\item 2021 Manish Gupta$^\dagger$, Mechanical and Aerospace Engineering, Syracuse University, {\it ``Molecular Interfaces and Heterogeneous Bubble Nucleation from Heated Surfaces at Nanoscale".} (Advisor: Dr.~Shalabh C. Maroo)
%\item 2021 Justin King$^\dagger$, Mechanical Aerospace Engineering, Syracuse University, {\it ``The Influence of Trailing Edge Shape and Kinematics on Bio-inspired Pitching Panels".} (Advisor: Dr.~Melissa Green)
%\end{myitemize}

%M.S. degree:\\
%$~~~~~~$???? Sriram Srinivasan, Aerospace Engineering, Syracuse University\\
%$~~~~~~$???? Sareta R. Gladson, Aerospace Engineering, Syracuse University\\

\end{document}

